\textsc{geepers}: Principal Stratification using Principal Scores and Stacked Estimating Equations

### 2023-11-03 writeUps/outcomeRegAppendix.tex
add class FE, replicable appendix tables

\begin{table}

@@

\begin{tabular}{l c c c c}

@@

(Intercept)                                        & $-2.14$       & $1.73$      & $2.83^{***}$ & $2.51^{**}$  \\
                                                   & $(1.26)$      & $(0.92)$    & $(0.72)$     & $(0.92)$     \\
Scale.Score5                                       & $-0.59^{**}$  & $0.21$      & $0.45^{***}$ & $0.05$       \\
                                                   & $(0.19)$      & $(0.13)$    & $(0.10)$     & $(0.13)$     \\
ESOL1                                              & $-0.83$       & $0.09$      & $-0.46$      & $-0.49$      \\
                                                   & $(0.64)$      & $(0.36)$    & $(0.27)$     & $(0.35)$     \\
IEP1                                               & $-1.34^{**}$  & $0.15$      & $0.23$       & $0.10$       \\
                                                   & $(0.46)$      & $(0.29)$    & $(0.25)$     & $(0.28)$     \\
pre.total\_time\_on\_tasks                         & $-0.45^{**}$  & $-0.13$     & $0.08$       & $-0.00$      \\
                                                   & $(0.15)$      & $(0.09)$    & $(0.07)$     & $(0.10)$     \\
pre\_MSE\_total\_score                             & $-0.18$       & $0.20^{*}$  & $0.12$       & $0.35^{***}$ \\
                                                   & $(0.13)$      & $(0.08)$    & $(0.07)$     & $(0.08)$     \\
fullYear5TRUE                                      & $1.40^{*}$    & $-0.13$     & $-0.10$      & $0.06$       \\
                                                   & $(0.58)$      & $(0.33)$    & $(0.29)$     & $(0.34)$     \\
pre\_MA\_total\_scoreNATRUE                        & $-3.20^{***}$ &             &              &              \\
                                                   & $(0.71)$      &             &              &              \\
GenderM                                            & $0.17$        & $-0.19$     & $-0.34^{**}$ & $-0.27$      \\
                                                   & $(0.25)$      & $(0.15)$    & $(0.13)$     & $(0.16)$     \\
raceEthHispanic/Latino                             & $-0.56$       & $0.28$      & $0.33$       & $0.23$       \\
                                                   & $(0.46)$      & $(0.29)$    & $(0.21)$     & $(0.28)$     \\
raceEthAsian                                       & $-0.43$       & $0.66^{*}$  & $0.62^{**}$  & $0.82^{**}$  \\
                                                   & $(0.42)$      & $(0.28)$    & $(0.22)$     & $(0.30)$     \\
raceEthOther                                       & $-0.13$       & $0.45$      & $0.21$       & $0.10$       \\
                                                   & $(0.49)$      & $(0.29)$    & $(0.23)$     & $(0.30)$     \\
GIFTED1                                            & $-0.24$       & $0.66^{**}$ & $0.43^{*}$   & $0.34$       \\
                                                   & $(0.37)$      & $(0.24)$    & $(0.19)$     & $(0.26)$     \\
poly(pre\_PS\_tasks\_total\_score, 2, raw = TRUE)1 & $0.01$        &             &              &              \\
                                                   & $(0.19)$      &             &              &              \\
poly(pre\_PS\_tasks\_total\_score, 2, raw = TRUE)2 & $-0.41^{**}$  &             &              &              \\
                                                   & $(0.13)$      &             &              &              \\
Z                                                  &               & $0.29$      & $-0.17$      & $-0.20$      \\
                                                   &               & $(0.28)$    & $(0.22)$     & $(0.27)$     \\
Sp                                                 &               & $0.03$      & $-0.22$      & $0.04$       \\
                                                   &               & $(0.52)$    & $(0.41)$     & $(0.52)$     \\
pre\_PS\_tasks\_total\_score                       &               & $0.34^{**}$ & $0.37^{***}$ & $0.23$       \\
                                                   &               & $(0.12)$    & $(0.09)$     & $(0.12)$     \\
pre.total\_math\_score                             &               & $0.14^{**}$ & $0.24^{***}$ & $0.15^{**}$  \\
                                                   &               & $(0.05)$    & $(0.04)$     & $(0.05)$     \\
pre.total\_math\_scoreNATRUE                       &               & $-0.35$     & $0.18$       & $-0.44$      \\
                                                   &               & $(0.45)$    & $(0.36)$     & $(0.43)$     \\
Z:Sp                                               &               & $-0.14$     & $0.17$       & $-0.17$      \\
                                                   &               & $(0.49)$    & $(0.39)$     & $(0.49)$     \\

@@

AIC                                                & $447.55$      & $$          & $$           & $$           \\
BIC                                                & $539.47$      & $$          & $$           & $$           \\
Log Likelihood                                     & $-200.78$     & $$          & $$           & $$           \\
Deviance                                           & $401.55$      & $$          & $$           & $$           \\
R$^2$                                              & $$            & $0.60$      & $0.60$       & $0.63$       \\
Adj. R$^2$                                         & $$            & $0.52$      & $0.55$       & $0.54$       \\

@@

\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}

@@

@@

\end{table}

>>>>

\usepackage{longtable}

@@

\begin{longtable}{l c c c c}

@@

\endfirsthead

@@

@@

\endhead
\endfoot
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}\\

@@

\endlastfoot \\
(Intercept)                                        & $-7.75$      & $5.64^{*}$   & $7.43^{***}$ & $3.65$       \\
                                                   & $(5.04)$     & $(2.47)$     & $(1.82)$     & $(2.35)$     \\
GenderM                                            & $0.21$       & $-0.26$      & $-0.30^{*}$  & $-0.16$      \\
                                                   & $(0.28)$     & $(0.15)$     & $(0.13)$     & $(0.16)$     \\
raceEthHispanic/Latino                             & $-0.54$      & $-0.02$      & $0.43^{*}$   & $0.41$       \\
                                                   & $(0.50)$     & $(0.28)$     & $(0.21)$     & $(0.28)$     \\
raceEthAsian                                       & $-0.36$      & $0.54^{*}$   & $0.79^{***}$ & $0.63^{*}$   \\
                                                   & $(0.45)$     & $(0.25)$     & $(0.20)$     & $(0.26)$     \\
raceEthOther                                       & $-0.09$      & $0.37$       & $0.35$       & $-0.06$      \\
                                                   & $(0.54)$     & $(0.29)$     & $(0.23)$     & $(0.30)$     \\
Performance.Level5Developing Learner               & $-0.79$      & $-0.62$      & $-0.52$      & $-0.14$      \\
                                                   & $(0.95)$     & $(0.53)$     & $(0.39)$     & $(0.48)$     \\
Performance.Level5Distinguished Learner            & $-1.08$      & $-0.41$      & $0.11$       & $0.34$       \\
                                                   & $(1.23)$     & $(0.68)$     & $(0.54)$     & $(0.67)$     \\
Performance.Level5Proficient Learner               & $-1.08$      & $-0.27$      & $-0.20$      & $-0.09$      \\
                                                   & $(1.04)$     & $(0.58)$     & $(0.43)$     & $(0.53)$     \\
EIP1                                               & $0.50$       & $0.26$       & $0.09$       & $0.33$       \\
                                                   & $(0.73)$     & $(0.40)$     & $(0.31)$     & $(0.39)$     \\
Scale.Score5                                       & $-0.57$      & $0.48^{**}$  & $0.47^{**}$  & $0.28$       \\
                                                   & $(0.35)$     & $(0.18)$     & $(0.15)$     & $(0.19)$     \\
ESOL1                                              & $-1.01$      & $0.40$       & $-0.40$      & $-0.38$      \\
                                                   & $(0.70)$     & $(0.35)$     & $(0.26)$     & $(0.34)$     \\
GIFTED1                                            & $-0.26$      & $0.79^{***}$ & $0.62^{***}$ & $0.78^{**}$  \\
                                                   & $(0.41)$     & $(0.23)$     & $(0.18)$     & $(0.25)$     \\
IEP1                                               & $-1.46^{**}$ & $0.18$       & $0.24$       & $0.16$       \\
                                                   & $(0.51)$     & $(0.27)$     & $(0.24)$     & $(0.27)$     \\
IST1                                               & $-0.55$      & $-0.06$      & $0.14$       & $-0.46$      \\
                                                   & $(0.67)$     & $(0.36)$     & $(0.29)$     & $(0.38)$     \\
SECTION5041                                        & $0.42$       & $0.73$       & $0.58$       & $0.51$       \\
                                                   & $(0.92)$     & $(0.47)$     & $(0.39)$     & $(0.48)$     \\
SST1                                               & $-0.61$      & $-0.40$      & $0.14$       & $-0.77$      \\
                                                   & $(1.11)$     & $(0.58)$     & $(0.41)$     & $(0.51)$     \\
AbsentDays5                                        & $0.25$       & $-0.12$      & $-0.02$      & $-0.12$      \\
                                                   & $(0.27)$     & $(0.15)$     & $(0.12)$     & $(0.16)$     \\
UnexcusedDays5                                     & $-0.48$      & $0.24$       & $-0.00$      & $0.19$       \\
                                                   & $(0.40)$     & $(0.21)$     & $(0.18)$     & $(0.23)$     \\
AbsentDays6                                        & $-0.30$      & $0.04$       & $0.12$       & $0.04$       \\
                                                   & $(0.31)$     & $(0.17)$     & $(0.14)$     & $(0.17)$     \\
UnexcusedDays6                                     & $0.57$       &              &              &              \\
                                                   & $(0.32)$     &              &              &              \\
pre.total\_math\_score                             & $-0.05$      &              &              &              \\
                                                   & $(0.16)$     &              &              &              \\
pre.sub\_P\_score                                  & $-0.04$      & $-0.32^{*}$  & $-0.35^{**}$ & $-0.25$      \\
                                                   & $(0.24)$     & $(0.14)$     & $(0.11)$     & $(0.14)$     \\
pre.sub\_F\_score                                  & $0.12$       & $-0.38^{**}$ & $-0.28^{*}$  & $-0.32^{*}$  \\
                                                   & $(0.24)$     & $(0.14)$     & $(0.11)$     & $(0.14)$     \\
pre.math\_completed\_num                           & $0.73$       & $-0.15$      & $-0.06$      & $-0.10$      \\
                                                   & $(0.46)$     & $(0.19)$     & $(0.12)$     & $(0.16)$     \\
pre.total\_time\_on\_tasks                         & $-0.52^{**}$ & $-0.18$      & $0.11$       & $-0.07$      \\
                                                   & $(0.19)$     & $(0.10)$     & $(0.08)$     & $(0.10)$     \\
pre\_MA\_total\_score                              & $-0.01$      &              &              &              \\
                                                   & $(0.03)$     &              &              &              \\
pre\_MSE\_total\_score                             & $-0.15$      &              &              &              \\
                                                   & $(0.16)$     &              &              &              \\
pre\_PS\_part2E\_score                             & $0.17$       & $0.04$       & $0.06$       & $0.12$       \\
                                                   & $(0.20)$     & $(0.12)$     & $(0.09)$     & $(0.12)$     \\
pre\_PS\_part2NE\_score                            & $0.04$       & $0.24^{*}$   & $0.20^{*}$   & $0.04$       \\
                                                   & $(0.19)$     & $(0.11)$     & $(0.09)$     & $(0.11)$     \\
pre\_PS\_completed\_num                            & $-0.11$      & $-0.11^{*}$  & $-0.09^{*}$  & $-0.04$      \\
                                                   & $(0.09)$     & $(0.05)$     & $(0.04)$     & $(0.05)$     \\
pre\_PS\_total\_RT\_sec                            & $0.07$       & $0.17$       & $0.02$       & $0.21$       \\
                                                   & $(0.23)$     & $(0.13)$     & $(0.10)$     & $(0.13)$     \\
fullYear5TRUE                                      & $1.54^{*}$   & $-0.41$      & $-0.08$      & $-0.09$      \\
                                                   & $(0.62)$     & $(0.32)$     & $(0.28)$     & $(0.34)$     \\
fullYear6TRUE                                      & $0.65$       & $0.17$       & $-0.15$      & $0.50$       \\
                                                   & $(0.84)$     & $(0.42)$     & $(0.32)$     & $(0.42)$     \\
noUnexcused5TRUE                                   & $-0.23$      & $0.05$       & $-0.21$      & $-0.27$      \\
                                                   & $(0.52)$     & $(0.28)$     & $(0.23)$     & $(0.30)$     \\
Performance.Level5NATRUE                           & $0.15$       & $-0.22$      & $-0.25$      & $-0.05$      \\
                                                   & $(0.61)$     & $(0.33)$     & $(0.24)$     & $(0.32)$     \\
AbsentDays6NATRUE                                  & $-0.24$      & $-0.72$      & $-0.18$      & $0.11$       \\
                                                   & $(0.80)$     & $(0.45)$     & $(0.35)$     & $(0.45)$     \\
pre.total\_math\_scoreNATRUE                       & $3.23$       & $-1.66$      & $-0.99$      & $-0.77$      \\
                                                   & $(3.71)$     & $(1.12)$     & $(0.74)$     & $(1.10)$     \\
pre\_MA\_total\_scoreNATRUE                        & $-1.58$      & $-1.84^{*}$  & $-1.05$      & $-1.22$      \\
                                                   & $(1.59)$     & $(0.87)$     & $(0.56)$     & $(0.70)$     \\
poly(pre\_PS\_tasks\_total\_score, 2, raw = TRUE)1 & $-0.18$      & $0.12$       & $0.20$       & $0.00$       \\
                                                   & $(0.32)$     & $(0.18)$     & $(0.14)$     & $(0.18)$     \\
poly(pre\_PS\_tasks\_total\_score, 2, raw = TRUE)2 & $-0.41^{**}$ & $-0.05$      & $-0.07$      & $0.04$       \\
                                                   & $(0.14)$     & $(0.08)$     & $(0.06)$     & $(0.07)$     \\
Z                                                  &              & $0.33$       & $-0.17$      & $-0.33$      \\
                                                   &              & $(0.27)$     & $(0.23)$     & $(0.27)$     \\
Sp                                                 &              & $0.08$       & $-0.12$      & $0.04$       \\
                                                   &              & $(0.53)$     & $(0.45)$     & $(0.54)$     \\
ns(UnexcusedDays6, 3)1                             &              & $-1.17^{**}$ & $-1.03^{**}$ & $-0.95^{*}$  \\
                                                   &              & $(0.45)$     & $(0.37)$     & $(0.44)$     \\
ns(UnexcusedDays6, 3)2                             &              & $-0.57$      & $-0.29$      & $-0.70$      \\
                                                   &              & $(0.58)$     & $(0.51)$     & $(0.60)$     \\
ns(UnexcusedDays6, 3)3                             &              & $-0.70$      & $0.14$       & $-0.08$      \\
                                                   &              & $(0.60)$     & $(0.59)$     & $(0.64)$     \\
ns(pre\_MA\_total\_score, 3)1                      &              & $-0.16$      & $-0.42$      & $-0.15$      \\
                                                   &              & $(0.37)$     & $(0.29)$     & $(0.39)$     \\
ns(pre\_MA\_total\_score, 3)2                      &              & $-0.34$      & $-0.90$      & $1.20$       \\
                                                   &              & $(1.09)$     & $(0.85)$     & $(1.09)$     \\
ns(pre\_MA\_total\_score, 3)3                      &              & $-0.05$      & $0.02$       & $0.38$       \\
                                                   &              & $(0.49)$     & $(0.41)$     & $(0.54)$     \\
pre\_MSE\_total\_score $<$ -2TRUE                  &              & $0.93$       & $-0.79$      & $-0.21$      \\
                                                   &              & $(0.72)$     & $(0.58)$     & $(0.80)$     \\
ns(pre\_MSE\_total\_score, 3)1                     &              & $1.34$       & $-0.10$      & $0.96$       \\
                                                   &              & $(0.79)$     & $(0.65)$     & $(0.82)$     \\
ns(pre\_MSE\_total\_score, 3)2                     &              & $3.56$       & $-1.41$      & $2.29$       \\
                                                   &              & $(2.57)$     & $(2.20)$     & $(2.68)$     \\
ns(pre\_MSE\_total\_score, 3)3                     &              & $1.13$       & $-0.03$      & $1.00$       \\
                                                   &              & $(0.58)$     & $(0.45)$     & $(0.57)$     \\
ns(pre.total\_math\_score, 4)1                     &              & $1.04$       & $1.71^{***}$ & $0.84$       \\
                                                   &              & $(0.61)$     & $(0.47)$     & $(0.63)$     \\
ns(pre.total\_math\_score, 4)2                     &              & $2.62^{***}$ & $2.57^{***}$ & $2.77^{***}$ \\
                                                   &              & $(0.69)$     & $(0.53)$     & $(0.71)$     \\
ns(pre.total\_math\_score, 4)3                     &              & $4.54^{***}$ & $5.68^{***}$ & $5.28^{***}$ \\
                                                   &              & $(1.29)$     & $(1.04)$     & $(1.39)$     \\
ns(pre.total\_math\_score, 4)4                     &              & $3.47^{***}$ & $4.35^{***}$ & $3.19^{***}$ \\
                                                   &              & $(0.84)$     & $(0.64)$     & $(0.82)$     \\
Z:Sp                                               &              & $-0.16$      & $0.14$       & $-0.06$      \\
                                                   &              & $(0.48)$     & $(0.40)$     & $(0.49)$     \\
AIC                                                & $484.78$     & $$           & $$           & $$           \\
BIC                                                & $676.61$     & $$           & $$           & $$           \\
Log Likelihood                                     & $-194.39$    & $$           & $$           & $$           \\
Deviance                                           & $388.78$     & $$           & $$           & $$           \\
R$^2$                                              & $$           & $0.54$       & $0.57$       & $0.55$       \\
Adj. R$^2$                                         & $$           & $0.50$       & $0.55$       & $0.51$       \\
\end{longtable}

@@
